---
title: "SA 10 year bond sensitivity estimate"
format: 
  pptx:
    fig-pos: "H"
    dpi: 500
---



```{r}
library(readr)
library(here)
yields <- read_rds(here("Outputs", "artifacts_yields.rds"))
country <- read_rds(here("Outputs", "artifacts_country_comparison.rds"))
```


# Yields rose significantly in recent months 


```{r yields, echo = FALSE, message=FALSE, dpi=500}
yields$graphs$yield_gg
```





# The rolling window estimates suggests a marked increase in sensitivity

:::: {.columns}

::: {.column width="60%"}
```{r estimate, echo = FALSE, message=FALSE, dpi=500, fig.width=8}
yields$graphs$graphs_gg
```
:::

::: {.column width="40%"}
- The sample is from the year 2000 to September 2023 with a monthly frequency
- OLS estimates with a 36 month (3 year window) meaning that we estimate each month with 36 observations and roll until the end of the sample
- The post Covid period similar to the period post the financial crisis has seen a  significant increase in the sensitivity
:::

::::

```{r country, echo = FALSE, message=FALSE, dpi=500, fig.width=8}

```

# Country comparison


```{r country1, echo = FALSE, message=FALSE, dpi=500, fig.width=10}
country$graphs$combined_yield_gg 
```

# Country 1

```{r country2, echo = FALSE, message=FALSE, dpi=500, fig.width=8}       
country$graphs$ols_full_gg
```

# Country 2
```{r country3, echo = FALSE, message=FALSE, dpi=500, fig.width=8}
country$graphs$graphs_gg
```

# Country 3

```{r country4, echo = FALSE, message=FALSE, dpi=500, fig.width=6}
country$graphs$sensitivity_range_gg
```